---
title: "Kane's Free High School Data Science Bootcamp"
site: distill::distill_website
---

```{r setup, include=FALSE}
library(gapminder)
library(tidyverse)
library(gganimate)
library(htmltools)

knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

# Learn more about publishing to GitHub Pages at:
# https://rstudio.github.io/distill/publish_website.html#github-pages
```

[Sign up for our e-mail list](https://davidkane.substack.com/embed) to receive updates as we move forward.

```{r animation, cache = TRUE}
read_rds("animation.rds")
```

**Kane's Free High School Data Science Bootcamp** will run from Tuesday, June 1st through Friday, June 25th. The expected workload is 13 hours per week: 2.5 hours in class with [Harvard Preceptor David Kane](https://www.davidkane.info/), lecturing live at around 8:00 PM EDT and 10.5 hours of work completed by students on their own. By the end of this bootcamp, students will be able to do basic data science! The course covers the first three weeks or so in Kane's introductory data science class, [Gov 1005: Data](https://www.davidkane.info/files/gov_1005_spring_2021.html).

There are no prerequisites. The programming language we will be using is R. You must have a computer with R, RStudio and Git [installed](https://happygitwithr.com). 

[Sign up for our e-mail list](https://davidkane.substack.com/embed) to receive updates as we move forward.


