---
title: "Kane's Data Science Course"
site: distill::distill_website
---

```{r setup, include=FALSE}
library(gapminder)
library(tidyverse)
library(gganimate)
library(htmltools)

knitr::opts_chunk$set(echo = FALSE)
```

[Sign up for our e-mail list](https://davidkane.substack.com/embed) to receive updates going forward. 

**Kane's (Free) Data Science Course** is offered occasionally, always running four weeks. The current sessions started on Monday, June 13, 2022. The workload is 10 hours per week: 2 hours in class with [former Harvard Preceptor David Kane](https://www.davidkane.info/), lecturing live at around 8:00 PM EDT and 8 hours of work completed by students on their own. By the end of this course, students will be able to do basic data science! The course is for high school students, but those a bit younger or older are welcome. There is no charge.


```{r animation, cache = TRUE}
read_rds("animation.rds")
```


Check out the [final projects](https://bootcamp.davidkane.info/projects.html) created by prior students. See [here](https://davidkane9.github.io/bootcamp_june_2021/) for an archive of material from the June 2021 iteration of the Course.


There are no prerequisites. The programming language we will be using is R. You must have a computer with R, RStudio and Git [installed](https://happygitwithr.com). The course is designed for absolute beginners. No programming or statistics experience is required.

[Sign up for our e-mail list](https://davidkane.substack.com/embed) to receive updates.


